Topological Equivariant Artist Model

### 2022-02-21 slides/main.tex
reworking notation and pushpull story and finishing out Q

@@

    \frametitle<6|handout:2>{Data Bundle}
    \frametitle<7|handout:3>{Graphic Bundle}

@@

              \onslide*<7|handout:3>{\gfiberc} 
              \onslide*<4-|handout:1->{\arrow[r, hook]} \& 

@@

              \onslide*<7|handout:3>{\gtotalc}
              \onslide*<4-|handout:1->{\arrow[d, "\pi"']} \\

@@

               \onslide*<7|handout:3>{\gbasec} 

@@

               \onslide*<7|handout:3>{\arrow[u, "\gsectionc \in \cgamma{\opensetgc}{\gtotalc\restriction_{\opensetgc}}"', bend right, pos=.5]}

@@

        \only<7|handout:3>{

@@

        \end{description}    
    \end{alertblock}
    }
\end{frame}

\begin{comment}
    \note{move this to top where I introduce data/graphics}
\begin{frame}{Domain and Range}
    \begin{figure}
        \begin{subfigure}{.5\textwidth}
            \includegraphics[.5\textwidth]{../paper/figures/fiberbundle.png}
        \end{subfigure}
        \begin{subfigure}{.5\textwidth}
            \includegraphics[.5\textwidth]{../paper/figures/render.png}
        \end{subfigure}
    \end{figure}
\end{frame}
\end{comment}

\subsection{Category Theory}
\begin{frame}[fragile]{}
    \begin{minted}{python}
        Artist(data:Data) -> Graphic
    \end{minted}
\end{frame}

@@

@@

\begin{frame}{Sheaves} 
    A sheaf is a presheaf that satisfies the following two axioms\cite{bakerMathsSheaf}\\
    \begin{block}<2-|handout:1>{locality}
        \onslide<3-|handout:1>{
        given $\opensetc = \bigcup\limits_{i\in I} \opensetc_i$ and $\dsectionc^{a}, \dsectionc^{b} \in \sheafc(\opensetc)$,}
        \onslide<4|handout:1>{\\
        if $\dsectionc^{a}\restriction_{\opensetc_i} = \dsectionc^{b}\restriction_{\opensetc_i}$ for each $\opensetc_i \in \opensetc$}
        \onslide<4|handout:1>{then $\dsectionc^{a} = \dsectionc^{b}$}
    \end{block} 
    \begin{block}<5-|handout:1>{gluing} 
         given $\dsectionc^{i} \in \sheafc(\opensetc_i)$
        \onslide<6-|handout:1>{s.t. ${\dsectionc^{i}}\restriction_{\opensetc_i\cap \opensetc_j} = {\dsectionc^{j}}\restriction_{\opensetc_i \cap \opensetc_j}$ for $\opensetc_i, \opensetc_j \in \opensetc$,}
        \onslide<7-|handout:1>{\\there exists $\dsectionc \in \sheafc(\opensetc)$ such that $\dsectionc\restriction_{\opensetc_i} = {\dsectionc^{i}}$} 
    \end{block}      
\end{frame}

@@

            \item $\vindexpushc\gsectionc(\gbasepointc) = \gsectionc\restriction_{\vindexpre(\dbasepointc)} = \gsectionc(\gbasepointc) \forall \gbasepointc \in \vindexpre(\dbasepointc)$ 

@@

%add transition slide->possibly call back 
\begin{frame}
    {\huge
        \begin{equation*}
            \sheafc_{\dbasec,\dtotalc} \textcolor{artist}{\xrightarrow{\vartistc}} \sheafc_{\gbasec, \gtotalc}
        \end{equation*}
    }
\end{frame}

\begin{frame}{Natural Transformation $\textcolor{nattran}{\alpha}: \textcolor{functor}{F} \textcolor{nattran}{\Rightarrow} \textcolor{functor}{G}$}

    \adjustbox{scale=3, center}{
        \begin{tikzcd}[ampersand replacement=\&]
            \& {} \arrow[dd, "\alpha" , Rightarrow, shorten=1.5em, color=nattran] \&             \\
          \textcolor{source}{\mathcal{C}} \arrow[rr, "F", bend left, color=functor, maps to] \arrow[rr, "G"', bend right, color=functor, maps to] \& \& \textcolor{target}{\mathcal{D}} \\
            \& {} \&            
          \end{tikzcd}}
\end{frame}

\begin{frame}
    \frametitle<1-2|handout:1>{Data Space: $\vartistc_{\opensetc}: \sheafc_{\dbasec, \dtotalc} \textcolor{artist}{\Rightarrow} \vindexpushc\sheafc_{\gbasec, \gtotalc}$}
    \frametitle<3-4|handout:2>{Display Space: $\vartist_{\opensetgc}: \vindexpullc\sheafc_{\dbasec, \dtotalc} \textcolor{artist}{\Rightarrow} \sheafc_{\gbasec, \gtotalc}$}
    \frametitle<5|handout:3->{\textcolor{artist}{Artist} \vartistc}

    \onslide*<1|handout:1>{
        \begin{equation*}
      \begin{tikzcd}[ampersand replacement =\&]
        \cgamma{\opensetc_1}{\dtotalc} 
        \arrow[dd, "\iota^*"', hook, color=set] 
        \arrow[rrrr, "\vartistc_{\opensetc_1}", bend left, color=artist, Rightarrow] \&  \& 
        \opensetc_1 
        \arrow[ll, "\sheafc_{\dtotalc}", color=sheaf, maps to] 
        \arrow[rr, "\sheafc_{\gtotalpushc}"', color=sheaf, maps to] \&  \& 
        \cgamma{\opensetc_1}{\gtotalpushc} 
        \arrow[dd, "\iota^*", hook', color=set] \\
        {} 
        \arrow[rrrr, dotted, color=artist,Rightarrow] \&\&\&\& {} \\
        \cgamma{\opensetc_2}{\dtotalc} 
        \arrow[rrrr, "\vartistc_{\opensetc_2}"', bend right, color=artist, Rightarrow] \&  \& 
        \opensetc_2 
        \arrow[ll, "\sheafc_{\dtotalc}"', color=sheaf, maps to] 
        \arrow[rr, "\sheafc_{\gtotalpushc}", color=sheaf, maps to] 
        \arrow[uu, "\iota" description, hook, color=base] \& \& 
        \cgamma{\opensetc_2}{\gtotalpushc}               
    \end{tikzcd}
        \end{equation*}}

    \onslide*<0|handout:2>{
        \begin{equation*}
    \begin{tikzcd}[ampersand replacement =\&]
    \cgamma{\opensetgc_1}{\dtotalpullc} 
    \arrow[dd, "\iota^*"', hook, color=set] 
    \arrow[rrrr, "\vartistc_{\opensetgc_1}", bend left, color=artist, Rightarrow] \&  \& 
    \opensetgc_1 
    \arrow[ll, "\sheafc_{\dtotalpullc}", color=sheaf, maps to] 
    \arrow[rr, "\sheafc_{\gtotalc}"', color=sheaf, maps to] \&  \& 
    \cgamma{\opensetgc_1}{\gtotalc} 
    \arrow[dd, "\iota^*", hook', color=set] \\
    {} 
    \arrow[rrrr, dotted, color=artist, Rightarrow] \&\&\&\& {} \\
    \cgamma{\opensetgc_2}{\dtotalpullc} 
    \arrow[rrrr, "\vartistc_{\opensetgc_2}"', bend right, color=artist, Rightarrow] \&  \& 
    \opensetgc_2 
    \arrow[ll, "\sheafc_{\dtotalpullc}"', color=sheaf, maps to] 
    \arrow[rr, "\sheafc_{\gtotalc}", color=sheaf, maps to] 
    \arrow[uu, "\iota" description, hook, color=base] \& \& 
    \cgamma{\opensetgc_2}{\gtotalc}   
    \end{tikzcd}
    \end{equation*}}

    \begin{equation*}
        \begin{tikzcd}[ampersand replacement=\&]
          \onslide*<0|handout:3->{\sheafc_{\gbasec, \gtotalc}} 
          \onslide*<0|handout:3->{\arrow[rr, "\textcolor{functor}{\vindexpush}", color=functor]}  
          \& \& 
          \onslide*<0|handout:3->{\textcolor{functor}{\vindexpush}\sheafc_{\gbasec, \gtotalc}}
          \\
          \& \& \\
          \onslide*<0|handout:3->{\textcolor{functor}{\vindexpull}\sheafc_{\dbasec, \dtotalc}}
          \onslide*<0|handout:3->{\arrow[uu, "\vartistc_{\opensetgc}", color=artist, Rightarrow]}
          \&  \& 
          \onslide*<0|handout:3->{\sheafc_{\dbasec, \dtotalc}}
          \onslide*<0|handout:3->{\arrow[ll, "\textcolor{functor}{\vindexpull}", color=functor]} 
          \onslide*<0|handout:3->{\arrow[uu, "\vartistc_{\opensetc}"', color=artist, Rightarrow]}
          \onslide*<4-|handout:3->{\arrow[lluu, "\vartistc"' description, dashed, color=artist, Rightarrow]}
        \end{tikzcd}
      \end{equation*}

    \onslide<0|handout:3>{
        \begin{equation*}
        \textcolor{nattran}{Nat}_{\opensetgc}(\textcolor{functor}{\vindexpull}\sheafc_{\dbasec, \dtotalc}, \sheafc_{\gbasec, \gtotalc}) = 
    \textcolor{nattran}{Nat}_{\opensetc}(\sheafc_{\dbasec, \dtotalc}, \textcolor{functor}{\vindexpush}\sheafc_{\gbasec, \gtotalc})
        \end{equation*}
    }
    \onslide<0|handout:4>{
        \begin{equation*}
            \sheafc_{\dbasec, \dtotalc} \textcolor{artist}{\xrightarrow{\vartistc}} \sheafc_{\gbasec, \gtotalc}
        \end{equation*}
        \begin{equation*}
             (\sheafc_{\dbasec,\dtotalc} \textcolor{functor}{\xmapsto{\vindexpullc}} \vindexpullc \sheafc_{\dbasec,\dtotalc}) \textcolor{artist}{\xRightarrow{\vartistc_{\opensetgc}}} \sheafc_{\gbasec, \gtotalc} \tag{$\vartistc_{\opensetgc} \circ \vindexpullc = \vartistc$}
        \end{equation*}
        \begin{equation*}
            (\sheafc_{\dbasec,\dtotalc} \textcolor{artist}{\xRightarrow{\vartistc}} \sheafc_{\gbasec, \gtotalc}) \textcolor{functor}{\xmapsto{\vindexpushc}} \vindexpushc \sheafc_{\gbasec, \gtotalc} \tag{$\vindexpushc \circ \vartistc = \vartistc_{\opensetc}$}      
        \end{equation*}
        \begin{equation*}
            ((\sheafc_{\dbasec,\dtotalc} \textcolor{functor}{\xmapsto{\vindexpullc}} \vindexpullc \sheafc_{\dbasec,\dtotalc}) \textcolor{artist}{\xRightarrow{\vartistc_{\opensetgc}}} \sheafc_{\gbasec, \gtotalc})\textcolor{functor}{\xmapsto{\vindexpushc}} \vindexpushc \sheafc_{\gbasec, \gtotalc} \tag{$\vindexpushc \circ \vartistc_{\opensetgc} \circ \vindexpullc = \vartistc_{\opensetc}$}
        \end{equation*}
        }
\end{frame}

\begin{frame}{Output}
    \begin{equation*}
        \begin{tikzcd}[ampersand replacement=\&, row sep=huge]
            \cgamma{\opensetc}{\dtotalc\restriction_{\opensetc}} 
            \arrow[rr, "\vartistc", Rightarrow, color=artist] \&  \& 
            \cgamma{\opensetgc}{\gtotalc\restriction_{\opensetgc}} 
            \arrow[rrd, "\delta"'] 
            \arrow[rr, "render"] \&  \& visualization 
            \arrow[d, "measure" description] \\ 
            \&  \&  \&  \& M
            \end{tikzcd}
    \end{equation*}
\end{frame}

@@

\begin{frame}{Checking if \vartistc\ is equivariant}
    \begin{equation*}
        \begin{tikzcd}[ampersand replacement=\&]
            \cgamma{\opensetc}{\dtotalc\restriction_{\opensetc}} 
            \arrow[rr, "\vartistc"', Rightarrow, color=artist] 
            \arrow[d, "\dfuncc_{\dtotalc}"', color=action] 
            \arrow[rrr, "\equivc", bend left, color=monoid, dashed] \&  \& 
            \cgamma{\opensetgc}{\gtotalc\restriction_{\opensetgc}} 
            \arrow[r, "\delta"']\& M 
            \arrow[d, "\dfuncc_{M}", color=action] \\
            \cgamma{\opensetc^{\prime}}{\dfuncpullc\dtotalc\restriction_{\opensetc^{\prime}}} 
            \arrow[rr, "\vartistc", Rightarrow, color=artist] 
            \arrow[rrr, "\equivc"', bend right, color=monoid, dashed] \&  \& 
            \cgamma{\opensetgc^{\prime}}{\dfuncpullc\gtotalc\restriction_{\opensetgc^{\prime}}} 
            \arrow[r, "\delta"] \& M^{\prime}                        
        \end{tikzcd}
    \end{equation*}
        there exists a monoid homomorphism $\equivc: \dfuncc_{\dtotalc} \rightarrow \dfuncc_{M}$ such that 
        \begin{description}
            \item[equivariance] $\equivc(\dfuncc_{\dtotalc}(\dsectionc(\dbasepointc))) = \dfuncc_{M}(\equivc(\dsectionc(\dbasepointc)))$, for all $\dbasepointc \in \dbasec$ 
            \item[continuity] $\lim\limits_{x\to \dbasepointc}(\equivc(\dsectionc(x))) = \equivc(\dsectionc(\dbasepointc))$ for all $\dbasepointc \in \dbasec$ 
        \end{description} 
\end{frame}

\section{Complex Structure}
\begin{frame}{Multiple Bundles: $\dfuncc = (\dfunchc, \prod\limits_{i=0}^{n}\dfunctc_i)$} 
    \begin{equation*}
        \begin{tikzcd}[ampersand replacement = \&, column sep=2ex]
                \dfunctc_0 \circ \dfuncpullc \dtotalc_0 
                \arrow[rdd, "\pi" description] 
                \arrow[r, "\cdots \otimes \cdots", phantom] \& 
                \dfunctc_i \circ \dfuncpullc \dtotalc_i 
                \arrow[dd, "\pi" description] 
                \arrow[r, "\cdots \otimes \cdots", phantom] \& 
                \dfunctc_n \circ \dfuncpullc \dtotalc_n 
                \arrow[ldd, "\pi" description] \& = \& 
                \prod\limits_{i=0}^{n} 
                \dfunctc_i \circ \dfuncpullc \dtotalc 
                \arrow[dd, "\pi" description] \\    
                \&\&\&\&\\    
                \& 
                {(\dfunchc=\dfunchc_{i \in [0,n]}) \circ \dbasec }                                             \& \& = \& 
                \dfunchc \circ \dbasec                                                        
                \end{tikzcd}                                              
    \end{equation*}

@@

\begin{frame}{"Valid" viz?}
    \begin{equation*}
        \label{eq:artist:artist_sheaf}
        \begin{tikzcd}[ampersand replacement = \&, column sep=tiny, row sep=huge]
            \onslide*<1-|handout:1>{\cgamma{\opensetgc}{\gtotalc\restriction_{\opensetgc}}} 
            \&  \& 
            \onslide*<2-|handout:1>{\textcolor{set}{\big\{}\gsectionc:\opensetgc\rightarrow \gtotalc\restriction_{\opensetgc} 
              \bigm{\vert} \delta(\vartistc(\dsectionc)) = \equivc(\dsectionc) \textcolor{set}{\big\}}} 
            \onslide*<2-|handout:1>{\arrow[ll, "\textcolor{set}{\mathlarger{\mathlarger{\supset}}}" description, hook', color=white]} \\ 
            \&  \& \\
            \onslide*<1-|handout:1>{\opensetgc} 
            \onslide*<1-|handout:1>{\arrow[uu, "\sheafc_{\gtotalc}", color=sheaf, maps to]} 
            \onslide*<2-|handout:1>{\arrow[rruu, "\vartistc(\sheafc_{\dtotalc})\coloneqq \sheafc_{\vartistc}" description, dashed, color=sheaf, maps to]} 
            \&  \& 
        \end{tikzcd}
    \end{equation*}
\end{frame}

@@

    \begin{alertblock}{Build in Equivariance}
    implement $\vchannelc$ as a functor such that 
        \begin{description}
            \item[equivariance] $\vchannelc(\dfuncc_{\dtotalc}(\dsectionc(\dbasepointc))) = \dfuncc_{\vtotalc}(\vchannelc(\dsectionc(\dbasepointc)))$, for all $\dbasepointc \in \dbasec$ 
            \item[continuity] $\lim\limits_{x\to \dbasepointc}(\vchannelc(\dsectionc(x))) = \vchannelc(\dsectionc(\dbasepointc))$ for all $\dbasepointc \in \dbasec$ \note{for all sections} 
    \end{description} 
\end{alertblock}
\end{frame}

@@

\begin{frame}{Remapping Components}
    \begin{block}<>{Functor $\vchannel$}
        $\vchannelc$ is a functor from on fiber categories $\vchannel: \mathcal{\dfiberc} \rightarrow \mathcal{\vfiberc}$

\begin{frame}{Components to Graphic}
    \begin{figure}
        \includegraphics{../paper/figures/q_hat.p}
    \end{figure}
\end{frame}

>>>>

\subsection{Fiber Bundles}

@@

    \frametitle<6|handout:2-3>{Data Bundle}
    \frametitle<7|handout:4-5>{Graphic Bundle}

@@

              \onslide*<7|handout:4>{\gfiberc} 
              \onslide*<4-|handout:1-2,4>{\arrow[r, hook]} \& 

@@

              \onslide*<7|handout:4>{\gtotalc}
              \onslide*<4-|handout:1-2,4>{\arrow[d, "\pi"']} \\

@@

               \onslide*<7|handout:4>{\gbasec} 

@@

               \onslide*<7|handout:4>{\arrow[u, "\gsectionc \in \cgamma{\opensetgc}{\gtotalc\restriction_{\opensetgc}}"', bend right, pos=.5]}

@@

        \only<7|handout:4>{

@@

        \end{description}    
    \end{alertblock}
    }
    \only<|handout:3>{
        \begin{figure}
            \includegraphics[scale=.65]{figures/math/spherebundle.png}
        \end{figure}
    }
    \only<|handout:5>{
        \begin{figure}
            \includegraphics[scale=.65]{figures/math/render.png}
        \end{figure}
    }
\end{frame}

\subsection{Category Theory Language}
\begin{frame}[fragile]{}
    \begin{minted}{python}
        Artist(data:Data) -> Graphic
    \end{minted}
\end{frame}

@@

\begin{frame}{Natural Transformation $\textcolor{nattran}{\alpha}: \textcolor{functor}{F} \textcolor{nattran}{\Rightarrow} \textcolor{functor}{G}$}
    \onslide<|handout:1>{
    \adjustbox{scale=3, center}{
        \begin{tikzcd}[ampersand replacement=\&]
            \& {} \arrow[dd, "\alpha" , Rightarrow, shorten=1.5em, color=nattran] \&             \\
          \textcolor{source}{\mathcal{C}} \arrow[rr, "F", bend left, color=functor, maps to] \arrow[rr, "G"', bend right, color=functor, maps to] \& \& \textcolor{target}{\mathcal{D}} \\
            \& {} \&            
          \end{tikzcd}}}
\end{frame}

\subsection{Sheaves}

@@

\begin{frame}{Sheaves on Bundles} 
    A sheaf is a presheaf that satisfies the following two axioms\cite{bakerMathsSheaf}\\
    \begin{block}<2-|handout:1>{locality}
        \onslide<3-|handout:1>{
        given $\opensetc = \bigcup\limits_{i\in I} \opensetc_i$ and $\dsectionc^{a}, \dsectionc^{b} \in \sheafc(\opensetc)$,}
        \onslide<4|handout:1>{\\
        if $\dsectionc^{a}\restriction_{\opensetc_i} = \dsectionc^{b}\restriction_{\opensetc_i}$ for each $\opensetc_i \in \opensetc$}
        \onslide<4|handout:1>{then $\dsectionc^{a} = \dsectionc^{b}$}
    \end{block} 
    \begin{block}<5-|handout:1>{gluing} 
         given $\dsectionc^{i} \in \sheafc(\opensetc_i)$
        \onslide<6-|handout:1>{s.t. ${\dsectionc^{i}}\restriction_{\opensetc_i\cap \opensetc_j} = {\dsectionc^{j}}\restriction_{\opensetc_i \cap \opensetc_j}$ for $\opensetc_i, \opensetc_j \in \opensetc$,}
        \onslide<7-|handout:1>{\\there exists $\dsectionc \in \sheafc(\opensetc)$ such that $\dsectionc\restriction_{\opensetc_i} = {\dsectionc^{i}}$} 
    \end{block}      
\end{frame}

@@

            \item $\vindexpushc\gsectionc(\dbasepointc) = \gsectionc\restriction_{\vindexpre(\dbasepointc)} = \gsectionc(\gbasepointc) \forall \gbasepointc \in \vindexpre(\dbasepointc)$ 

@@

%add transition slide->possibly call back 
\subsection{Artist}
\begin{frame}
    \frametitle<0|handout:1>{Artist: \vartistc: \sheafc_{\dbasec, \dtotalc} \rightarrow \sheafc_{\gbasec, \gotalc}}
    \frametitle<0|handout:2>{Data Space: $\vartistc_{\opensetc}: \sheafc_{\dbasec, \dtotalc} \textcolor{artist}{\Rightarrow} \vindexpushc\sheafc_{\gbasec, \gtotalc}$}
    \frametitle<0|handout:3>{Display Space: $\vartist_{\opensetgc}: \vindexpullc\sheafc_{\dbasec, \dtotalc} \textcolor{artist}{\Rightarrow} \sheafc_{\gbasec, \gtotalc}$}
    \frametitle<0|handout:4>{Artist: \vartistc: \cgamma{\opensetc}{\dtotalc} \rightarrow \cgamma{\opensetgc}{\gtotalc}}
    \begin{equation*}
        \begin{tikzcd}[ampersand replacement=\&]
          \onslide*<0|handout:1>{\sheafc_{\gbasec, \gtotalc}} 
          \onslide*<0|handout:4>{\cgamma{\opensetgc}{\gtotalc\restriction_{\opensetgc}}}
          \onslide*<0|handout:1,4>{\arrow[rr, "\textcolor{functor}{\vindexpush}", color=functor]}  
          \& \& 
          \onslide*<0|handout:1>{\vindexpushc\sheafc_{\gbasec, \gtotalc}}
          \onslide*<0|handout:4>{\cgamma{\opensetc}{\vindexpushc \gtotalc\restriction_{\opensetc}}}
          \\
          \& \& \\
          \onslide*<0|handout:1>{\textcolor{functor}{\vindexpull}\sheafc_{\dbasec, \dtotalc}}
          \onslide*<0|handout:4>{\cgamma{\opensetgc}{\vindexpullc \dtotalc\restriction_{\opensetgc}}}
          \onslide*<0|handout:1,4>{\arrow[uu, "\vartistc_{\opensetgc}", color=artist, Rightarrow]}
          \&  \& 
          \onslide*<0|handout:1>{\sheafc_{\dbasec, \dtotalc}}
          \onslide*<0|handout:4>{\cgamma{\opensetc}{\dtotalc\restriction_{\opensetc}}}
          \onslide*<0|handout:1,4>{\arrow[ll, "\textcolor{functor}{\vindexpull}", color=functor]} 
          \onslide*<0|handout:1,4>{\arrow[uu, "\vartistc_{\opensetc}"', color=artist, Rightarrow]}
          \onslide*<4-|handout:1,4>{\arrow[lluu, "\vartistc"' description, dashed, color=artist, Rightarrow]}
        \end{tikzcd}
      \end{equation*}

      \onslide*<1|handout:2>{
        \begin{equation*}
      \begin{tikzcd}[ampersand replacement =\&]
        \cgamma{\opensetc_1}{\dtotalc} 
        \arrow[dd, "\iota^*"', hook, color=set] 
        \arrow[rrrr, "\vartistc_{\opensetc_1}", bend left, color=artist, Rightarrow] \&  \& 
        \opensetc_1 
        \arrow[ll, "\sheafc_{\dbasec,\dtotalc}", color=sheaf, maps to] 
        \arrow[rr, "\sheafc_{\dbasec,\gtotalpushc}"', color=sheaf, maps to] \&  \& 
        \cgamma{\opensetc_1}{\gtotalpushc} 
        \arrow[dd, "\iota^*", hook', color=set] \\
        {} 
        \arrow[rrrr, dotted, color=artist,Rightarrow] \&\&\&\& {} \\
        \cgamma{\opensetc_2}{\dtotalc} 
        \arrow[rrrr, "\vartistc_{\opensetc_2}"', bend right, color=artist, Rightarrow] \&  \& 
        \opensetc_2 
        \arrow[ll, "\sheafc_{\dbasec,\dtotalc}"', color=sheaf, maps to] 
        \arrow[rr, "\sheafc_{\dbasec,\gtotalpushc}", color=sheaf, maps to] 
        \arrow[uu, "\iota" description, hook, color=base] \& \& 
        \cgamma{\opensetc_2}{\gtotalpushc}               
    \end{tikzcd}
        \end{equation*}}

    \onslide*<0|handout:3>{
        \begin{equation*}
    \begin{tikzcd}[ampersand replacement =\&]
    \cgamma{\opensetgc_1}{\dtotalpullc} 
    \arrow[dd, "\iota^*"', hook, color=set] 
    \arrow[rrrr, "\vartistc_{\opensetgc_1}", bend left, color=artist, Rightarrow] \&  \& 
    \opensetgc_1 
    \arrow[ll, "\sheafc_{\gbasec, \dtotalpullc}", color=sheaf, maps to] 
    \arrow[rr, "\sheafc_{\gbasec,\gtotalc}"', color=sheaf, maps to] \&  \& 
    \cgamma{\opensetgc_1}{\gtotalc} 
    \arrow[dd, "\iota^*", hook', color=set] \\
    {} 
    \arrow[rrrr, dotted, color=artist, Rightarrow] \&\&\&\& {} \\
    \cgamma{\opensetgc_2}{\dtotalpullc} 
    \arrow[rrrr, "\vartistc_{\opensetgc_2}"', bend right, color=artist, Rightarrow] \&  \& 
    \opensetgc_2 
    \arrow[ll, "\sheafc_{\gbasec,\dtotalpullc}"', color=sheaf, maps to] 
    \arrow[rr, "\sheafc_{\gbasec, \gtotalc}", color=sheaf, maps to] 
    \arrow[uu, "\iota" description, hook, color=base] \& \& 
    \cgamma{\opensetgc_2}{\gtotalc}   
    \end{tikzcd}
    \end{equation*}}    
    \onslide<0|handout:1>{
        \begin{equation*}
        \textcolor{nattran}{Nat}_{\opensetgc}(\textcolor{functor}{\vindexpull}\sheafc_{\dbasec, \dtotalc}, \sheafc_{\gbasec, \gtotalc}) = 
    \textcolor{nattran}{Nat}_{\opensetc}(\sheafc_{\dbasec, \dtotalc}, \textcolor{functor}{\vindexpush}\sheafc_{\gbasec, \gtotalc})
        \end{equation*}
    }
    \onslide<0|handout:4>{
        \begin{alertblock}{pull data section \dsectionc\ over graphic space $\gbasepointc \in \gbasec$}
            $\vindexpullc\dsectionc(\gbasepointc) = \dsectionc(\vindexc(\gbasepointc)) = \dsectionc(\dbasepointc)$
        \end{alertblock}
        \begin{alertblock}{push graphic \gsectionc\ section over data space $\dbasepointc \in \dbasec$}
            $\vindexpushc\gsectionc(\dbasepointc) = \gsectionc\restriction_{\vindexpre(\dbasepointc)} = \gsectionc(\gbasepointc) \forall \gbasepointc \in \vindexpre(\dbasepointc)$ 
        \end{alertblock}
        }
\end{frame}

\begin{frame}{Artist as Profunctor}
    \begin{tikzcd}[ampersand replacement=\&]
        \cgamma{\opensetc}{\dtotalc\restriction_{\opensetc}}
        \arrow[rr, "\vartistc", Rightarrow, color=artist] 
        \&  \& \
        \cgamma{\opensetgc}{\dtotalc\restriction_{\opensetgc}}\\
        \& \&                                                                                 \\
        \opensetc 
        \arrow[uu, "{\sheafc_{\dbasec, \dtotalc}}", maps to, color=sheaf] 
        \&  \& 
        \opensetgc 
        \arrow[ll, "\vindexc"', color=functor] 
        \arrow[uu, "{\sheafc_{\gbasec, \gtotalc}}"', maps to, color=sheaf]
        \end{tikzcd}
\end{frame}

@@

\begin{frame}{Checking if \vartistc\ is equivariant}
    \begin{equation*}
        \begin{tikzcd}[ampersand replacement=\&, row sep=huge]
            \cgamma{\opensetc}{\dtotalc\restriction_{\opensetc}} 
            \arrow[rr, "\vartistc", Rightarrow, color=artist] \&  \& 
            \cgamma{\opensetgc}{\gtotalc\restriction_{\opensetgc}} 
            \arrow[rrd, "\delta"'] 
            \arrow[rr, "render"] \&  \& visualization 
            \arrow[d, "measure" description] \\ 
            \&  \&  \&  \& M
            \end{tikzcd}
    \end{equation*}
\end{frame}

\begin{frame}{Checking if \vartistc\ is equivariant}
    \begin{equation*}
        \begin{tikzcd}[ampersand replacement=\&]
            \cgamma{\opensetc}{\dtotalc\restriction_{\opensetc}} 
            \arrow[rr, "\vartistc"', Rightarrow, color=artist] 
            \arrow[d, "\dfuncc_{\dtotalc}"', color=action] 
            \arrow[rrr, "\equivc", bend left, color=monoid, dashed] \&  \& 
            \cgamma{\opensetgc}{\gtotalc\restriction_{\opensetgc}} 
            \arrow[r, "\delta"']\& M 
            \arrow[d, "\dfuncc_{M}", color=action] \\
            \cgamma{\opensetc^{\prime}}{\dfuncpullc\dtotalc\restriction_{\opensetc^{\prime}}} 
            \arrow[rr, "\vartistc", Rightarrow, color=artist] 
            \arrow[rrr, "\equivc"', bend right, color=monoid, dashed] \&  \& 
            \cgamma{\opensetgc^{\prime}}{\dfuncpullc\gtotalc\restriction_{\opensetgc^{\prime}}} 
            \arrow[r, "\delta"] \& M^{\prime}                        
        \end{tikzcd}
    \end{equation*}
        there exists a functor $\equivc: \dfuncc_{\dtotalc} \rightarrow \dfuncc_{M}$ such that 
        \begin{description}
            \item[equivariance] $\equivc(\dfuncc_{\dtotalc}(\dsectionc(\dbasepointc))) = \dfuncc_{M}(\equivc(\dsectionc(\dbasepointc)))$, for all $\dbasepointc \in \dbasec$ 
            \item[continuity] $\lim\limits_{x\to \dbasepointc}(\equivc(\dsectionc(x))) = \equivc(\dsectionc(\dbasepointc))$ for all $\dbasepointc \in \dbasec$ 
        \end{description} 
\end{frame}

\section{Complex Structure}
\begin{frame}{Multiple Bundles: $\dfuncc = (\dfunchc, \prod\limits_{i=0}^{n}\dfunctc_i)$} 
    \begin{equation*}
        \begin{tikzcd}[ampersand replacement = \&, column sep=2ex]
                \dfunctc_0 \dfuncpullc \dtotalc_0 
                \arrow[rdd, "\pi" description] 
                \arrow[r, "\cdots \otimes \cdots", phantom] \& 
                \dfunctc_i  \dfuncpullc \dtotalc_i 
                \arrow[dd, "\pi" description] 
                \arrow[r, "\cdots \otimes \cdots", phantom] \& 
                \dfunctc_n \dfuncpullc \dtotalc_n 
                \arrow[ldd, "\pi" description] \& = \& 
                \prod\limits_{i=0}^{n} 
                \dfunctc_i \dfuncpullc \dtotalc 
                \arrow[dd, "\pi" description] \\    
                \&\&\&\&\\    
                \& 
                {(\dfunchc=\dfunchc_{i \in [0,n]})\dbasec }                                             \& \& = \& 
                \dfunchc \dbasec                                                        
                \end{tikzcd}                                              
    \end{equation*}

@@

\begin{frame}{"Valid" viz?}
    \begin{equation*}
        \label{eq:artist:artist_sheaf}
        \begin{tikzcd}[ampersand replacement = \&, column sep=tiny, row sep=huge]
            \onslide*<1-|handout:1>{\cgamma{\opensetgc}{\gtotalc\restriction_{\opensetgc}}} 
            \&  \& 
            \onslide*<2-|handout:1>{\textcolor{set}{\big\{}\gsectionc 
              \bigm{\vert} \delta(\vartistc(\dfuncc_{\dtotalc}(\dsectionc))) = \dfuncc_{M}(\delta(\gsectionc)) \textcolor{set}{\big\}}} 
            \onslide*<2-|handout:1>{\arrow[ll, "\textcolor{set}{\mathlarger{\mathlarger{\supset}}}" description, hook', color=white]} \\ 
            \&  \& \\
            \onslide*<1-|handout:1>{\opensetgc} 
            \onslide*<1-|handout:1>{\arrow[uu, "\sheafc_{\gbasec,\gtotalc}", color=sheaf, maps to]} 
            \onslide*<2-|handout:1>{\arrow[rruu, "\vartistc(\sheafc_{\dtotalc})\coloneqq \sheafc_{\vartistc}" description, dashed, color=sheaf, maps to]} 
            \&  \& 
        \end{tikzcd}
    \end{equation*}
\end{frame}

@@

    \begin{alertblock}{Build in Equivariance}
    implement $\vchannelc$ as a functor such that 
        \begin{description}
            \item[equivariance] $\vchannelc(\dfuncc_{\dtotalc}(\dsectionc(\dbasepointc))) = \dfuncc_{\vtotalc}(\vchannelc(\dsectionc(\dbasepointc)))$, for all $\dbasepointc \in \dbasec$ 
            \item[continuity] $\lim\limits_{x\to \dbasepointc}(\vchannelc(\dsectionc(x))) = \vchannelc(\dsectionc(\dbasepointc))$ for all $\dbasepointc \in \dbasec$ \note{for all sections} 
    \end{description} 
\end{alertblock}
\end{frame}
\begin{frame}{Remapping Components}
    \begin{block}<>{Functor $\vchannel$}
        $\vchannelc$ is a functor from on fiber categories $\vchannelc: \mathcal{\dfiberc} \rightarrow \mathcal{\vfiberc}$

@@

\begin{frame}{Combining Components}
    \begin{tikzcd}[ampersand replacement = \&]
    \cgamma{\opensetc}{\dtotalc\restriction_{\opensetc}} 
    \arrow[r, "\vchannelc", color=artist] \& 
    \cgamma{\opensetc}{\vtotalc\restriction_{\opensetc}} 
    \arrow[r, "\vmarkc_*", color=artist] 
    \arrow[rr, "\vmarkc", bend left, color=artist] \& 
    \cgamma{\opensetc}{\vindexpushc\gtotalc\restriction_{\opensetc}} \& 
    \cgamma{\opensetgc}{\gtotalc\restriction_{\opensetgc}} 
    \arrow[l, "\vindexpushc"', color=functor, dashed]\\ 
    \& \\ \& 
    \opensetc 
    \arrow[luu, "{\sheafc_{\dbasec, \dtotalc}}" description, maps to, color=sheaf] 
    \arrow[uu, "{\sheafc_{\dbasec, \vtotalc}}" description, maps to, color=sheaf] 
    \arrow[ruu, "{\sheafc_{\dbasec, \gtotalc}}" description, maps to, color=sheaf] 
    \& \& 
    \opensetgc 
    \arrow[uu, "{\sheafc_{\gbasec, \gtotalc}}" description, maps to, color=sheaf] 
    \arrow[ll, "\vindexc"', dashed, color=functor]
    \end{tikzcd}
